---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

Load data using read.csv and assign to a variable so the expression is evaluated to unit and nothing is renderend by knitr.

```{r}
activities <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

```{r}
stepsPerDay <- aggregate(steps ~ date, activities, sum)
```

1 - Visualize the histogram of the total number of steps taken each day
9717 277 103 117 183 263
```{r}
hist(stepsPerDay$steps)
```

2 - The mean number of steps taken per day is `r mean(stepsPerDay$steps)` and the median total number of steps taken per day is `r median(stepsPerDay$steps)`

## What is the average daily activity pattern?

1 - A time series of the 5-minute interval

```{r}
meanStepsPerInterval <- aggregate(steps ~ interval, activities, mean)
plot(meanStepsPerInterval$interval, meanStepsPerInterval$steps, type = "l")
```

2 - Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps `r meanStepsPerInterval$interval[which.max(meanStepsPerInterval$steps)]`

## Imputing missing values

1 - The total number of missing values in the dataset is `r sum(is.na(activities$step))`

2 - We will use the mean steps per interval to replace NAs

3 - Create a new dataset

```{r}
newd <- activities
newd$steps = replace(newd$steps, is.na(newd$steps), meanStepsPerInterval$step)
```

4- Make a histogram

```{r}
newStepsPerDay <- aggregate(steps ~ date, newd, sum)
hist(newStepsPerDay$steps)
```

The new mean number of steps taken per day is `r mean(newStepsPerDay$steps)` and the new median total number of steps taken per day is `r median(newStepsPerDay$steps)`

Yes values differ from the first part of the assignment but not much.

## Are there differences in activity patterns between weekdays and weekends?
